---
title: "Optional week 3 assignment"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question: Based on your analysis, would you conclude that there is a significant association between college major category and income?
```{r, echo = FALSE}
library(collegeIncome)
data(college)
```

create data frame with major_category and median earnings per row
```{r}
cat <- college$major_category
earn <- college$median
df <- data.frame(cat, earn)
head(df)
```

provide aggregate means per category and sort to see signifcant changes between categories
```{r}
agg <- aggregate(df$earn ~ df$cat, df, mean)
agg <- agg[order(agg$`df$earn`, decreasing = TRUE),]
agg
```

Relevel the factors for the lowest income ("Interdisciplinary") and fit a model for the data 
```{r}
df$cat <- relevel(df$cat, ref = "Interdisciplinary")
fit <- lm(df$earn ~ df$cat)
summary(fit)
```
Summary shows that there is no signifcant change in income for categories as compared to the lowest income level

Boxplot of categories
```{r}
boxplot(df$earn ~  df$cat, las = 2)
```

